Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-21 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{thm}{Theorem}

@@

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
In general, each two real 1-dimensional projectors~$\proj{\psi_{0}}$
and $\proj{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$
might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
in the Hilbert space of dimension 3\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
in the Hilbert space of dimension 3. In general, we could discuss
all 1-dimensional projectors in any dimension. However, restricting
to $\mathbb{R}^{3}$ enable us to use cross product which will simplify
our discussion a lot, and $\mathbb{R}^{3}$ is easy to visualize and
imagine. Also, if a quantum IVPM~$\bar{\mu}$ has an empty core when
restricting to $\mathbb{R}^{3}$, $\bar{\mu}$ has an empty core on
the original space as well. So restricting on real 1-dimensional projectors
still provides valid results.

@@

\begin{definition}A function~$\bar{f}:S^{d-1}\rightarrow\mathscr{I}$
or $\bar{f}:\mathbb{C}S^{d-1}\rightarrow\mathscr{I}$ is called a
\emph{real} or \emph{complex interval-valued approximation frame function}\end{definition}

>>>>

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

@@

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure~$\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure~$\bar{\mu}$
might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
In general, each two real 1-dimensional projectors~$\proj{\psi_{0}}$
and $\proj{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$
might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
in the Hilbert space of dimension 3\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
in the Hilbert space of dimension 3. In general, we could discuss
all 1-dimensional projectors in any dimension. However, restricting
to $\mathbb{R}^{3}$ enable us to use cross product which will simplify
our discussion a lot, and $\mathbb{R}^{3}$ is easy to visualize and
imagine. Also, if a quantum IVPM~$\bar{\mu}$ has an empty core when
restricting to $\mathbb{R}^{3}$, $\bar{\mu}$ has an empty core on
the original space as well. So restricting on real 1-dimensional projectors
still provides valid results.

@@

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}For
any quantum probability measure~$\mu$ on the Hilbert space of dimension
3, we can define a \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
rule, the frame function of $\mu_{\phi}^{B}$ is denoted by $f_{\phi}^{B}$.\end{definition}

\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}A
frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
the following properties:
\begin{itemize}
\item $\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)=1$ for any orthonormal
basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\end{itemize}
Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the above properties, $f$ must be a frame function.\end{lemma}

\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
space of dimension 3, we can define an \emph{interval-valued frame
function} $\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
The left-end and the right-end of an interval-valued frame function
are $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfying $\bar{f}\left(\ket{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
respectively.\end{definition}
